Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-01 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

Structures that would have been missed, if just one single technique alone would have been used: 
\textsf{
\begin{tabular}[c]{p{6cm}|p{3cm}|p{3.75cm}}
\label{tab:missing_structures}
What? & visible in fig.~\ref{fig:SICM_STED1} by SICM & visible in fig.~\ref{fig:SICM_STED1} by STED microscopy \\ \hline
The connections between the small round cell with the protrusion and the other cells & \textbf{PARTLY} & YES \\ \hline
The full extent of the protrusion & YES & \textbf{NO} \\ \hline
The connection between the roundish and the flat cell & \textbf{NO} & YES \\
\end{tabular}}

@@

>>>>

Structures that would have been missed and/or could have been misinterpreted, if just one single
technique alone would have been used: 
\textsf{
\begin{tabular}[c]{p{6cm}|p{3cm}|p{3.75cm}}
\label{tab:missing_structures}
What? & visible in fig.~\ref{fig:SICM_STED1} by SICM & visible in fig.~\ref{fig:SICM_STED1} by STED microscopy \\ \hline
The connections between the small round cell with the protrusion and the other cells & \textbf{PARTLY} & YES \\ \hline
The full extent of the protrusion & YES & \textbf{NO} \\ \hline
The connection between the roundish and the flat cell & \textbf{NO} & YES \\
\end{tabular}}

@@

As mentioned in section~\ref{}, SICM was also successfully combined with dSTORM (see 
section~\ref{sec:deterministic-approaches}) \cite{Hennig2015_nanoinj}. The difference to the 
SICM/STED microscopy correlation study was, that the SICM was there used for nanoinjecting 
fluorescently labeled molecules $-$ ATTO 655-phalloidin $-$ into living U2OS cells.

% Hier jetzt noch was zu SICM/SNOM!
